Evolution of Methodologies in Delivering Reliable Software in the European Scientific Arena

### 2018-06-01 paper-ieee-trans.tex
reviers comments

\usepackage{graphicx}
\usepackage{array}
\usepackage{subfigure}
\usepackage{adjustbox}
\usepackage{listings}
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % \DeclareGraphicsExtensions{.eps}
\fi

@@

\IEEEPARstart{D}uring the last 15 years the provision of an European e--Infrastructure,
supporting unified access to large--scale computing and intense data analysis
applications, has been driven by the needs of scientific communities as part of their
pan--European research collaborations. One such example is the Worldwide
Large Hadron Collider (LHC) Computing Grid infrastructure, driven
by the particle physics scientific community, built to satisfy the computing needs
of processing, storing and analysis of the very large amount of data produced by the
% Comment from reviewer
%(Update: I see this is discussed later... so it would be good just to signpost at the start that a) the focus is really on "grids", and b) that specific examples will be given.
LHC particle accelerator. A significant number of innovation projects and
technology transfer activities -- from the European Commission (EC)-funded 5th, 6th and 7th Framework Programmes,
and recently from the Horizon 2020 programme \cite{h2020} -- have as their main goal to
develop software solutions that provide a seamless and transparent access of researchers to distributed
computing and data resources.

@@

\bibitem{egi-qc}
\emph{EGI Quality Criteria} [Online]. Available: http://egi-qc.github.io/ .

>>>>

\usepackage{graphicx}
\usepackage{array}
\usepackage{subfigure}
\usepackage{adjustbox}
\usepackage{listings}
\usepackage{url}
\usepackage{cite}
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % \DeclareGraphicsExtensions{.eps}
\fi

@@

\IEEEPARstart{D}{uring} the last 15 years the provision of an European e--Infrastructure,
supporting unified access to large--scale computing and intense data analysis
applications, has been driven by the needs of scientific communities as part of their
pan--European research collaborations. One such example is the Worldwide
Large Hadron Collider (LHC) Computing Grid infrastructure, driven
by the particle physics scientific community, built to satisfy the computing needs
of processing, storing and analysis of the very large amount of data produced by the
% Comment from reviewer
%(Update: I see this is discussed later... so it would be good just to signpost at the start that a) the focus is really on "grids", and b) that specific examples will be given.
LHC particle accelerator. A significant number of innovation projects and
technology transfer activities -- from the European Commission (EC)-funded 5th, 6th and 7th Framework Programmes,
and recently from the Horizon 2020 programme \cite{h2020} -- have as their main goal to
develop software solutions that provide a seamless and transparent access of researchers to distributed
computing and data resources.

@@
